Concurrent Programming in Harmony

### 2021-08-17 book/paper.tex
Added a few more problems

Method \texttt{incrementer} takes a parameter called \textit{self}.
It increments \textit{count} and sets \textit{done}[\textit{self}] to \textbf{True}.
It then waits until the other thread is done.
(\textbf{await} $c$ is shorthand for \textbf{while not} $c$: \textbf{pass}) and semantically the same.
After that, method \texttt{incrementer}
verifies that the value of \textit{count} equals~2.
% Like Python, Harmony supports \textbf{assert} statements with two arguments:
% the first is a Boolean condition, and the second is a value that is
% reported if the condition fails, in this case
% the value of \textit{count}.

@@

\section*{Exercises}
\begin{problems}
\item Perhaps the trickiest detail of the algorithm is that, in Line~14
of \autoref{fig:paxos2}, the leader selects the proposal with the highest
ballot number it receives.  Replace the \texttt{max} operator in that statement
with \texttt{choose} and see if it finds a problem.  First try with
$\texttt{NBALLOTS} = 2$ and then with $\texttt{NBALLOTS} = 3$.
(Warning, the latter may take a long time.)  If it finds a problem,
analyze the output and see what went wrong.
\end{problems}

@@

>>>>

Method \texttt{incrementer} takes a parameter called \textit{self}.
It increments \textit{count} and sets \textit{done}[\textit{self}] to \textbf{True}.
It then waits until the other thread is done.
(\textbf{await} $c$ is shorthand for \textbf{while not} $c$: \textbf{pass}.)
After that, method \texttt{incrementer}
verifies that the value of \textit{count} equals~2.
% Like Python, Harmony supports \textbf{assert} statements with two arguments:
% the first is a Boolean condition, and the second is a value that is
% reported if the condition fails, in this case
% the value of \textit{count}.

@@

\section*{Exercises}
\begin{problems}
\item Perhaps the trickiest detail of the algorithm is that, in Line~14
of \autoref{fig:paxos2}, the leader selects the proposal with the highest
ballot number it receives.  Replace the \texttt{max} operator in that statement
with \texttt{choose} and see if it finds a problem.  First try with
$\texttt{NBALLOTS} = 2$ and then with $\texttt{NBALLOTS} = 3$.
(Warning, the latter may take a long time.)  If it finds a problem,
analyze the output and see what went wrong.
\item \cite{MWA19} discusses a buggy version of Paxos.  In this version,
the responses to the second phase are matched not by ballot number but
by the value of the proposal.  Implement this version and, using Harmony,
find the problem this causes.
\end{problems}

@@

\section*{Exercises}
\begin{problems}
\item Figure out how to fix the protocol.
\item There were two versions of the Needham-Schroeder protocol: the
Symmetric Key protocol and the Public Key protocol.  In this chapter
we only discussed the latter, but the former also had a problem.  See
if you can find it using Harmony.
\end{problems}
